---
title: "data_monthly_v1_0_EDA"
output: "pdf_document"
editor_options: 
  chunk_output_type: inline
---

# 0. Preparation
## Load Libraries
```{r, message=FALSE, warning=FALSE}
# Load libraries
library(tidyverse)
library(Hmisc)
library(gridExtra)
library(finalfit)
library(stargazer)
# To create and work with tidy temporal data
library(tsibble)
# To work with date-times and time-spans
library(lubridate)
# Provides a collection of commonly used univariate/multivariate TS models
library(fable)
## To interact directly with the Quandl API and download data
library(Quandl)
# For analyzing tidy time series data.
library(feasts)
# Provides methods and tools for displaying and analyzing univariate time series forecasts library(forecast)
# For estimation, lag selection, diagnostic testing, forecasting, and impulse response functions of VAR library(vars)
#provides tools for statistical calculations
library(stats)
# To assist the quantitative trader in the development,
#testing and deployment of statistically based trading models.
library(quantmod)
# For statistical analysis
library(car)
## To retrieve and display the information returned online by Google Trends
library(gtrendsR)
# To do time series analysis and computational finance.
library(tseries)
```

## Import data from csv file
Rows: 19015
Columns: 62

[Link to the handmade codebook](https://docs.google.com/spreadsheets/d/1-FQsF_sxnA6iBMNpHmGovkj9Xev6BCYg2j3PojNGgyk/edit?usp=sharing)
https://docs.google.com/spreadsheets/d/1-FQsF_sxnA6iBMNpHmGovkj9Xev6BCYg2j3PojNGgyk/edit?usp=sharing

## Overview of monthly dataset
```{r, message=FALSE, warning=FALSE}
raw_df <- read_csv("../../../data/datasets/data_monthly_v1_0.csv")
glimpse(raw_df)
```
# 1. Findings
## Source of each observation
All the observation seems to have origin in four datasets
```{r}
raw_df %>% 
  group_by(dataset) %>%
  summarise(count=n())
```
Sites are linked to dataset
```{r}
raw_df %>% 
  group_by(SITE_ID, dataset) %>%
  summarise(count=n())
```



--- 
## Distribution of Land-cover Type by Site
`SITE_IGBP`(Land-cover Type): 11
`SITE_ID`(Sites): 243
```{r}
raw_df %>% 
  count(SITE_ID)
```
```{r}
raw_df
```

```{r, fig.width=10, fig.height=3}
library(dplyr)
site_igbp_distribution <- raw_df %>% 
  dplyr::select(SITE_ID, SITE_IGBP) %>%
  group_by(SITE_IGBP) %>%
  summarise(count= n())

fig1 <- raw_df %>% 
  dplyr::select(SITE_ID,SITE_IGBP) %>%
  unique() %>%
  group_by(SITE_IGBP) %>%
  summarise(count=n()) %>%
  ggplot(aes(x=SITE_IGBP, y=count)) +
  geom_bar(stat='identity') +
  labs(title = "Distribution of land-cover type(sites)")

fig2 <- site_igbp_distribution %>% 
  ggplot(aes(x=SITE_IGBP, y=count)) +
  geom_bar(stat='identity') +
  labs(title = "Distribution of land-cover type(observations)")

grid.arrange(fig1, fig2, nrow = 1, ncol = 2)
```
```{r}
site_igbp_distribution
```

### Add features that distinguish northern/southern hemisphere
```{r}
raw_df_hemisphere <- raw_df %>%
  mutate(hemisphere = ifelse(LOCATION_LAT >= 0, "N", "S"))

raw_df_hemisphere
```
```{r, fig.width=10, fig.height=3}
library(dplyr)
site_igbp_distribution <- raw_df_hemisphere %>%
  
  dplyr::select(SITE_ID, SITE_IGBP) %>%
  group_by(SITE_IGBP) %>%
  summarise(count= n())

fig1 <- raw_df %>% 
  dplyr::select(SITE_ID,SITE_IGBP) %>%
  unique() %>%
  group_by(SITE_IGBP) %>%
  summarise(count=n()) %>%
  ggplot(aes(x=SITE_IGBP, y=count)) +
  geom_bar(stat='identity') +
  labs(title = "Distribution of land-cover type(sites)")

fig2 <- site_igbp_distribution %>% 
  ggplot(aes(x=SITE_IGBP, y=count)) +
  geom_bar(stat='identity') +
  labs(title = "Distribution of land-cover type(observations)")

grid.arrange(fig1, fig2, nrow = 1, ncol = 2)
```


## Observe categorical variables
Since they only have 243 rows by removing all the duplicates, 
all the categorical has unique values in each site.
```{r}
raw_df_categorical <- raw_df_hemisphere %>%
  dplyr::select(SITE_ID, SITE_IGBP, dataset, MODIS_IGBP, MODIS_PFT, 
         koppen_sub, koppen, hemisphere) %>% 
  distinct() #drop duplicates
  
head(raw_df_categorical)
```
```{r}
raw_df_categorical %>% 
  distinct(koppen) %>%
  as.list()
```

### Unique values of categorical variables

- SITE_ID: 243
- SITE_IGBP: 11
  - MF, ENF, GRA, SAV, WSA, EBF, WET, OSH, DBF, CRO, CSH
- MODIS_IGBP: 14 
  - OSH, SAV, MF, CSH, GRA, ENF, EBF, WSA, DBF, CRO, WAT, BSV, URB, WET
- MODIS_PFT: 14 
  -  SH, SA, MF, GRA, ENF, EBF, DBF, CRO, Other
- koppen_sub: 21
  - BSk, Cfa, Dfb, BWh, Aw, BWk, BSh, Csa, Cfb, Am, Dfc, Dwb, Dwa, Cwa, Dwc,
    ET, Dsb, Af, Dsc, Csb, Dfa
- koppen: 5
  - Arid, Temperate, Cold, Tropical, Polar

## Convert to monthly average dataset

### Create a new df of monthly average across sites(SITE_ID)
row: 2781

```{r}
SITE_month_df <- raw_df_hemisphere %>% 
  group_by(SITE_ID, SITE_IGBP, month) %>%
  summarise(TA_F_avg = mean(TA_F, na.rm = T),VPD_F_avg = mean(VPD_F, na.rm = T),
            P_F_avg = mean(P_F, na.rm = T),NETRAD_avg = mean(NETRAD, na.rm = T),
            NEE_VUT_REF_avg = mean(NEE_VUT_REF, na.rm = T),
            NEE_VUT_REF_QC_avg = mean(NEE_VUT_REF_QC, na.rm = T),
            NEE_CUT_REF_avg = mean(NEE_CUT_REF, na.rm = T),
            NEE_CUT_REF_QC_avg = mean(NEE_CUT_REF_QC, na.rm = T),
            GPP_NT_VUT_REF_avg = mean(GPP_NT_VUT_REF, na.rm = T),
            GPP_DT_VUT_REF_avg = mean(GPP_DT_VUT_REF, na.rm = T),
            GPP_NT_CUT_REF_avg = mean(GPP_NT_CUT_REF, na.rm = T),
            GPP_DT_CUT_REF_avg = mean(GPP_DT_CUT_REF, na.rm = T),
            RECO_NT_VUT_REF_avg = mean(RECO_NT_VUT_REF, na.rm = T),
            RECO_DT_VUT_REF_avg = mean(RECO_DT_VUT_REF, na.rm = T),
            RECO_NT_CUT_REF_avg = mean(RECO_NT_CUT_REF, na.rm = T),
            RECO_DT_CUT_REF_avg = mean(RECO_DT_CUT_REF, na.rm = T),
            ET_avg = mean(ET, na.rm = T),
            `BESS-PAR_avg` = mean(`BESS-PAR`, na.rm = T),
            `BESS-PARdiff_avg` = mean(`BESS-PARdiff`, na.rm = T),
            `BESS-RSDN_avg` = mean(`BESS-RSDN`, na.rm = T),
            `CSIF-SIFdaily_avg` = mean(`CSIF-SIFdaily`, na.rm = T),
            `CSIF-SIFinst_avg` = mean(`CSIF-SIFinst`, na.rm = T),
            PET_avg = mean(PET, na.rm = T),Ts_avg = mean(Ts, na.rm = T),
            Tmean_avg = mean(Tmean, na.rm = T),
            prcp_avg = mean(prcp, na.rm = T),
            vpd_avg = mean(vpd, na.rm = T),
            `prcp-lag3_avg` = mean(`prcp-lag3`, na.rm = T),
            `ESACCI-sm_avg` = mean(`ESACCI-sm`, na.rm = T),
            b1_avg = mean(b1, na.rm = T),b2_avg = mean(b2, na.rm = T),
            b3_avg = mean(b3, na.rm = T),b4_avg = mean(b4, na.rm = T),
            b5_avg = mean(b5, na.rm = T),b6_avg = mean(b6, na.rm = T),
            b7_avg = mean(b7, na.rm = T),EVI_avg = mean(EVI, na.rm = T),
            GCI_avg = mean(GCI, na.rm = T),NDVI_avg = mean(NDVI, na.rm = T),
            NDWI_avg = mean(NDWI, na.rm = T),NIRv_avg = mean(NIRv, na.rm = T),
            kNDVI_avg = mean(kNDVI, na.rm = T),
            Percent_Snow_avg = mean(Percent_Snow, na.rm = T),
            Fpar_avg = mean(Fpar, na.rm = T),Lai_avg = mean(Lai, na.rm = T),
            LST_Day_avg = mean(LST_Day, na.rm = T),
            LST_Night_avg = mean(LST_Night, na.rm = T),
            CO2_concentration_avg = mean(CO2_concentration, na.rm = T)
                        )

<<<<<<< HEAD
# Merge categorical variables

# raw_df_categorical_ <- raw_df_categorical %>%
#   dplyr::select(-c(SITE_IGBP)) # drop SITE_IGBP to avoid two variables in one df
# SITE_month_df <- merge(x = SITE_month_df, y = raw_df_categorical_,
#                        by="SITE_ID", all.x = TRUE)
# 
# # Add longitude/latitude to monthly df
# raw_df_geo <- raw_df_hemisphere %>% dplyr::select(SITE_ID, LOCATION_LAT, LOCATION_LONG)
# SITE_month_df <- merge(x = SITE_month_df, y = raw_df_geo,
#                        by="SITE_ID", all.x = TRUE)
# raw_df_ts_month <- raw_df %>% as_tsibble(index=month)
```


=======

# Merge categorical variables

raw_df_categorical_ <- raw_df_categorical %>%
  dplyr::select(-c(SITE_IGBP)) # drop SITE_IGBP to avoid two variables in one df
SITE_month_df <- merge(x = SITE_month_df, y = raw_df_categorical_,
                       by="SITE_ID", all.x = TRUE)

# Add longitude/latitude to monthly df
raw_df_geo <- raw_df_hemisphere %>% dplyr::select(SITE_ID, LOCATION_LAT, LOCATION_LONG)
SITE_month_df <- merge(x = SITE_month_df, y = raw_df_geo,
                       by="SITE_ID", all.x = TRUE)

# raw_df_ts_month <- raw_df %>% as_tsibble(index=month)
```

>>>>>>> 171dac32c3ec2e4066b788989a9e7554e681e5a7
## Create a new df of monthly average across land-cover types(SITE_IGBP)
Categorical variables are excluded due to its dependency to each site. 
```{r}
IGBP_month_df <- raw_df_hemisphere %>% 
  group_by(SITE_IGBP, hemisphere, month) %>%
  summarise(TA_F_avg = mean(TA_F, na.rm = T),VPD_F_avg = mean(VPD_F, na.rm = T),
            P_F_avg = mean(P_F, na.rm = T),NETRAD_avg = mean(NETRAD, na.rm = T),
            NEE_VUT_REF_avg = mean(NEE_VUT_REF, na.rm = T),
            NEE_VUT_REF_QC_avg = mean(NEE_VUT_REF_QC, na.rm = T),
            NEE_CUT_REF_avg = mean(NEE_CUT_REF, na.rm = T),
            NEE_CUT_REF_QC_avg = mean(NEE_CUT_REF_QC, na.rm = T),
            GPP_NT_VUT_REF_avg = mean(GPP_NT_VUT_REF, na.rm = T),
            GPP_DT_VUT_REF_avg = mean(GPP_DT_VUT_REF, na.rm = T),
            GPP_NT_CUT_REF_avg = mean(GPP_NT_CUT_REF, na.rm = T),
            GPP_DT_CUT_REF_avg = mean(GPP_DT_CUT_REF, na.rm = T),
            RECO_NT_VUT_REF_avg = mean(RECO_NT_VUT_REF, na.rm = T),
            RECO_DT_VUT_REF_avg = mean(RECO_DT_VUT_REF, na.rm = T),
            RECO_NT_CUT_REF_avg = mean(RECO_NT_CUT_REF, na.rm = T),
            RECO_DT_CUT_REF_avg = mean(RECO_DT_CUT_REF, na.rm = T),
            ET_avg = mean(ET, na.rm = T),
            `BESS-PAR_avg` = mean(`BESS-PAR`, na.rm = T),
            `BESS-PARdiff_avg` = mean(`BESS-PARdiff`, na.rm = T),
            `BESS-RSDN_avg` = mean(`BESS-RSDN`, na.rm = T),
            `CSIF-SIFdaily_avg` = mean(`CSIF-SIFdaily`, na.rm = T),
            `CSIF-SIFinst_avg` = mean(`CSIF-SIFinst`, na.rm = T),
            PET_avg = mean(PET, na.rm = T),Ts_avg = mean(Ts, na.rm = T),
            Tmean_avg = mean(Tmean, na.rm = T),
            prcp_avg = mean(prcp, na.rm = T),
            vpd_avg = mean(vpd, na.rm = T),
            `prcp-lag3_avg` = mean(`prcp-lag3`, na.rm = T),
            `ESACCI-sm_avg` = mean(`ESACCI-sm`, na.rm = T),
            b1_avg = mean(b1, na.rm = T),b2_avg = mean(b2, na.rm = T),
            b3_avg = mean(b3, na.rm = T),b4_avg = mean(b4, na.rm = T),
            b5_avg = mean(b5, na.rm = T),b6_avg = mean(b6, na.rm = T),
            b7_avg = mean(b7, na.rm = T),EVI_avg = mean(EVI, na.rm = T),
            GCI_avg = mean(GCI, na.rm = T),NDVI_avg = mean(NDVI, na.rm = T),
            NDWI_avg = mean(NDWI, na.rm = T),NIRv_avg = mean(NIRv, na.rm = T),
            kNDVI_avg = mean(kNDVI, na.rm = T),
            Percent_Snow_avg = mean(Percent_Snow, na.rm = T),
            Fpar_avg = mean(Fpar, na.rm = T),Lai_avg = mean(Lai, na.rm = T),
            LST_Day_avg = mean(LST_Day, na.rm = T),
            LST_Night_avg = mean(LST_Night, na.rm = T),
            CO2_concentration_avg = mean(CO2_concentration, na.rm = T)
                        )
# raw_df_ts_month <- raw_df %>% as_tsibble(index=month)
```
### Export df to csv
```{r}
<<<<<<< HEAD
write.csv(IGBP_month_df,
          "../../../data/datasets/SITE_IGBP_month_df.csv",row.names=FALSE)
write.csv(SITE_month_df,
          "../../../data/datasets/SITE_month_df.csv", row.names=FALSE)
=======
# write.csv(IGBP_month_df,
#           "../../../data/datasets/SITE_IGBP_month_df.csv",row.names=FALSE)
# write.csv(SITE_month_df,
#           "../../../data/datasets/SITE_month_df.csv", row.names=FALSE)
>>>>>>> 171dac32c3ec2e4066b788989a9e7554e681e5a7
```

# Monthly transition of GPP and NEE by land-cover type
```{r}
IGBP_month_df %>% group_by(SITE_IGBP,hemisphere) %>% summarise(count = n())
```

```{r, fig.height=4, fig.width=10}
library(scales)
f3 <- IGBP_month_df %>% subset(SITE_IGBP == "MF") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) + 
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("MF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f4 <- IGBP_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) + 
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("DBF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f5 <- IGBP_month_df %>% subset(SITE_IGBP == "CRO") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CRO") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f6 <- IGBP_month_df %>% subset(SITE_IGBP == "WET") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("WET") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f7 <- IGBP_month_df %>% subset(SITE_IGBP == "GRA") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("GRA") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f8 <- IGBP_month_df %>% subset(SITE_IGBP == "EBF") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) + 
  ggtitle("EBF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f9 <- IGBP_month_df %>% subset(SITE_IGBP == "OSH") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) + 
  ggtitle("OSH") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f10 <- IGBP_month_df %>% subset(SITE_IGBP == "WSA") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("WSA") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f11 <- IGBP_month_df %>% subset(SITE_IGBP == "SAV") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("SAV") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f12 <- IGBP_month_df %>% subset(SITE_IGBP == "CSH") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CSF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f13 <- IGBP_month_df %>% subset(SITE_IGBP == "ENF") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("ENF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)
f13  

grid.arrange(f3, f4, f5, f6, f7, f8, f9, f10, f11, f12, nrow = 2, ncol = 5)
  # gg_tsdisplay(GPP_DT_VUT_REF_avg, plot_type="partial")
```


```{r, fig.height=4, fig.width=10}
library(scales)
f13 <- IGBP_month_df %>% subset(SITE_IGBP == "MF") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) + 
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("MF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f14 <- IGBP_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) + 
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("DBF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f15 <- IGBP_month_df %>% subset(SITE_IGBP == "CRO") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CRO") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f16 <- IGBP_month_df %>% subset(SITE_IGBP == "WET") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("WET") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f17 <- IGBP_month_df %>% subset(SITE_IGBP == "GRA") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("GRA") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f18 <- IGBP_month_df %>% subset(SITE_IGBP == "EBF") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) + 
  ggtitle("EBF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f19 <- IGBP_month_df %>% subset(SITE_IGBP == "OSH") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +  
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) + 
  ggtitle("OSH") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f20 <- IGBP_month_df %>% subset(SITE_IGBP == "WSA") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("WSA") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f21 <- IGBP_month_df %>% subset(SITE_IGBP == "SAV") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("SAV") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f22 <- IGBP_month_df %>% subset(SITE_IGBP == "CSH") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) +   
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CSF") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f23 <- IGBP_month_df %>% subset(SITE_IGBP == "ENF") %>%
  subset(hemisphere == "N") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_VUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_VUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("ENF") +
  theme(# legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)
f23  

grid.arrange(f13, f14, f15, f16, f17, f18, f19, f20, f21, f22, nrow = 2, ncol = 5)
  # gg_tsdisplay(GPP_DT_VUT_REF_avg, plot_type="partial")
```
 
```{r}
SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  group_by(SITE_ID, SITE_IGBP) %>%
  summarise(count = n())
  
```
 
 
```{r, fig.height=4, fig.width=10}

f25 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "CA-Cbo") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CA-Cbo") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f26 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "CA-Oas") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CA-Oas") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f27 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "CA-TPD") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CA-TPD") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)


f28 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "CZ-Lnz") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CZ-Lnz") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f29 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "CZ-Stn") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("CZ-Stn") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)


f30 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "DE-Hai") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("DE-Hai") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f31 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "DE-HoH") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("DE-HoH") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)


f32 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "DE-Hzd") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("DE-Hzd") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f33 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "DE-Lnf") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("DE-Lnf") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

f34 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
  subset(SITE_ID == "DK-Sor") %>%
  ggplot(aes(x=month)) +
  geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
  geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
  scale_x_continuous(breaks= pretty_breaks()) +
  ggtitle("DK-Sor") +
  theme(legend.position="none",
        axis.title.x = element_text(size = 6),
        axis.title.y = element_text(size = 6),
        title = element_text(size = 8)) + ylim(0, 12.5)

# f34 <- SITE_month_df %>% subset(SITE_IGBP == "DBF") %>%
#   subset(SITE_ID == "CA-Oas") %>%
#   ggplot(aes(x=month)) +
#   geom_line(aes(y=GPP_DT_CUT_REF_avg, colour="DT")) + 
#   geom_line(aes(y=GPP_NT_CUT_REF_avg, colour="NT")) +
#   scale_x_continuous(breaks= pretty_breaks()) +
#   ggtitle("CA-Oas") +
#   theme(legend.position="none",
#         axis.title.x = element_text(size = 6),
#         axis.title.y = element_text(size = 6),
#         title = element_text(size = 8)) + ylim(0, 12.5)

grid.arrange(f25, f26, f27, f28, f29, f30, f31, f32, f33, f34, 
             nrow = 2, ncol = 5) #f34, 
```
 
 

```{r, fig.width=5, fig.height=3.5}
# GPP_DT_VUT_REF in DE-Seh
print("GPP_DT_VUT_REF in DE-Seh")
raw_df_hemisphere %>% subset(SITE_ID == "DE-Seh") %>%
  subset(hemisphere == "N") %>%
  mutate(time_to_date = yearmonth(as.Date(time, format = "%m/%d/%y"))) %>%
  as_tsibble(index = time_to_date) %>%
  tsibble::fill_gaps() %>%
  gg_tsdisplay(GPP_DT_VUT_REF, plot_type="partial")

# GPP_NT_VUT_REF in DE-Seh
print("GPP_NT_VUT_REF in DE-Seh")
raw_df_hemisphere %>% subset(SITE_ID == "DE-Seh") %>%
  subset(hemisphere == "N") %>%
  mutate(time_to_date = yearmonth(as.Date(time, format = "%m/%d/%y"))) %>%
  as_tsibble(index = time_to_date) %>%
  tsibble::fill_gaps() %>%
  gg_tsdisplay(GPP_NT_VUT_REF, plot_type="partial")
  
# NEE_VUT_REF in DE-Seh
print("NEE_VUT_REF in DE-Seh")
raw_df_hemisphere %>% subset(SITE_ID == "DE-Seh") %>%
  subset(hemisphere == "N") %>%
  mutate(time_to_date = yearmonth(as.Date(time, format = "%m/%d/%y"))) %>%
  as_tsibble(index = time_to_date) %>%
  tsibble::fill_gaps() %>%
  gg_tsdisplay(NEE_VUT_REF, plot_type="partial")

# NEE_VUT_REF_QC in DE-Seh
print("NEE_VUT_REF_QC in DE-Seh")
raw_df_hemisphere %>% subset(SITE_ID == "DE-Seh") %>%
  subset(hemisphere == "N") %>%
  mutate(time_to_date = yearmonth(as.Date(time, format = "%m/%d/%y"))) %>%
  as_tsibble(index = time_to_date) %>%
  tsibble::fill_gaps() %>%
  gg_tsdisplay(NEE_VUT_REF_QC, plot_type="partial")

```
```{r, fig.width=5, fig.height=4}
```


```{r}
IGBP_month_df %>% subset(SITE_IGBP == "CRO") %>%
  subset(hemisphere == "N") %>%
  as_tsibble(index = month) %>% 
  gg_tsdisplay(GPP_DT_VUT_REF_avg, plot_type="partial")
```
```{r}

```
```{r}

<<<<<<< HEAD
=======
```{r, fig.width=5, fig.height=3.5}
# GPP_DT_VUT_REF in DE-Seh
print("GPP_DT_VUT_REF in DE-Seh")
raw_df_hemisphere %>% subset(SITE_ID == "DE-Seh") %>%
  subset(hemisphere == "N") %>%
  mutate(time_to_date = yearmonth(as.Date(time, format = "%m/%d/%y"))) %>%
  as_tsibble(index = time_to_date) %>%
  tsibble::fill_gaps() %>%
  gg_tsdisplay(GPP_DT_VUT_REF, plot_type="partial")

# GPP_NT_VUT_REF in DE-Seh
print("GPP_NT_VUT_REF in DE-Seh")
raw_df_hemisphere %>% subset(SITE_ID == "DE-Seh") %>%
  subset(hemisphere == "N") %>%
  mutate(time_to_date = yearmonth(as.Date(time, format = "%m/%d/%y"))) %>%
  as_tsibble(index = time_to_date) %>%
  tsibble::fill_gaps() %>%
  gg_tsdisplay(GPP_NT_VUT_REF, plot_type="partial")
  
# NEE_VUT_REF in DE-Seh
print("NEE_VUT_REF in DE-Seh")
raw_df_hemisphere %>% subset(SITE_ID == "DE-Seh") %>%
  subset(hemisphere == "N") %>%
  mutate(time_to_date = yearmonth(as.Date(time, format = "%m/%d/%y"))) %>%
  as_tsibble(index = time_to_date) %>%
  tsibble::fill_gaps() %>%
  gg_tsdisplay(NEE_VUT_REF, plot_type="partial")

# NEE_VUT_REF_QC in DE-Seh
print("NEE_VUT_REF_QC in DE-Seh")
raw_df_hemisphere %>% subset(SITE_ID == "DE-Seh") %>%
  subset(hemisphere == "N") %>%
  mutate(time_to_date = yearmonth(as.Date(time, format = "%m/%d/%y"))) %>%
  as_tsibble(index = time_to_date) %>%
  tsibble::fill_gaps() %>%
  gg_tsdisplay(NEE_VUT_REF_QC, plot_type="partial")

```
```{r, fig.width=5, fig.height=4}
```


```{r}

```
```{r}

```
```{r}

>>>>>>> 171dac32c3ec2e4066b788989a9e7554e681e5a7
```

# Appendix
# Summary statistics of features
Rows: 19015
Columns: 62

```{r}
describe(raw_df)
```











